Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-11-03 manuscript.tex
20161103

\begin{abstract}
This paper presents a novel adaptive dynamic sliding mode scheme for the deployment of the tethered satellite system. \textcolor{red}{To overcome the limited inputs of the dynamic model, a new scalable dimensionless transformation and strictly bounded terms are designed, which guarantee the existence of the ratio between limited inputs and command signals.} The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain. The stability analysis indicates that this measure can eliminate the uncertainty caused by the input limitation and guarantee the asymptotically stability of the deployment dynamics. \textcolor{red}{Finally, numerical simulations are presented to verify the effectiveness of the proposed control laws.}
\end{abstract}
\begin{keyword}
Tethered satellite system;  Sliding mode control;  Input limitation; Adaptive control
\end{keyword}
\end{frontmatter}
\section{Introduction}
The deployment is the key technology of the space tethered satellite system (TSS)~\cite{wen2008advances,yousefian2015anti}, which supports various applications for space exploration and scientific research, such as space debris removals, space elevators, satellite de-orbits and the tethered space robots~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,huang2014optimal,Huang2016Impact,Huang201637,Huang2016}. \textcolor{red}{Many international space research institutes have launched some orbital, suborbital and ground experiments, such as TSS-1R, SEDS, MAST and YES2, in an effort to verify the feasibility of the proposed theoretical and simulation design for the deployment of the TSS~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}. These experimental results intensively help researchers proceed to promote advanced mechanics, kinetic and control studies, to tackle the future challenges of space activities~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line,Xu2016Hybrid}.}\par

\textcolor{red}{Recent scientific researches about deployment of the TSS focus on the stabilization of the dynamics, and have provided different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approaches~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}.} Among these stabilization strategies, the hybrid tension and thruster control technique has been a great boost to new developments of the deployment of the TSS. Iki et al. implemented the ground experiment of an electrodynamic tether deployment from a spool-type reel, and utilized the thruster to guarantee the deployment of kilometers-length space tether~\cite{iki2014experiments}. \textcolor{red}{Aslanov et al. presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system was excited by a thruster force acting on the tug~\cite{aslanov2013dynamics}.} Huang et al. investigated the attitude and deployment dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}. Jung et al. adopted thruster scheme to achieve the ideal deployment rate during the deployment of three-body tethered satellites~\cite{jung2015nonlinear}. \textcolor{red}{Liu et al. equipped the subsatellite with the thruster system, consisting of four pairs of thrusters, in order to regulate the attitude and deployment dynamics~\cite{liu2014attitude}. Zakrzhevskii divided the deployment process into two stages: in the first stage, the thruster was used to eject to the desired starting point of the next stage, and in the second stage, the tether was adjusted to the stable vertical configuration using tension generated by friction~\cite{zakrzhevskii2016method}. Mantellato et al. reported the thruster-aided deployment of tape tethers driven by both the tension and thruster force~\cite{mantellato2015thrust}. These hybrid strategies has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, and thus is broadly utilized in engineering applications compared with other control strategies.}\par

There also exist some obstacles in the hybrid control design. Particularly, it's a prime problem that tension actuators and thrusters are both constrained by physical and chemical conditions, i.e., the tether is not available to be repressed like the stick, and meanwhile too big tether length rate might break the space tether. Also, the thruster can not provide infinite force~\cite{martinez1998spacecraft}. Hence the tension and thruster force for the deployment/retrievial are both limited, and in the view of control theory, the phenomena usually causes the input limitation of a dynamic system. Substituting limited inputs into unmodified conventional control scheme designed for systems with unlimited inputs results in poor performance or instability, and theoretically, such kind of implement is unreasonable. Hence to cope with input limitation in the TSS, many scientific researchers spent much effort on restricting input, providing many solutions on satellite arrangements and deployments. Huang et al. proposed an adaptive postcapture backstepping control of the tethered space robot, and analyzed the effect of constrained input by using specific auxiliary design systems~\cite{huang2015adaptive}. Wen et al. took into account the positive bounded tension constraint by designing the feedback control with special saturation technique~\cite{wen2016constrained}, and Wen also proposed some remarkable achievements using optimal control for deployment~\cite{wen2008optimal}. Liu et al. reported the variable structure scheme for the deployment with thruster control, where the thruster is used to guarantee the positive tension during the mission~\cite{yingying2012variable}. In summary, existing studies deal with the major issue about the deployment with restricted tension and thruster force in two ways, accordingly, the suitable physical compensation and the elaborate design of limited input. In aspect of designing elaborate limited inputs, as Wen et al. explained, the limited terms, including the tension and the states of deployment dynamics, can be viewed as the solution of a nonlinear optimal control issue~\cite{wen2015tension}. \textcolor{red}{Hu reported an adaptive sliding mode control law with saturated input by using reduced sliding dynamic design approach~\cite{Hu2009Robust}, which requires an assumption that the command signal is bounded strictly, and for actual physical systems, this assumption always exits.} In this paper, a new dynamic adaptive saturated sliding mode  control for the deployment of the TSS is studied. For coping with the input saturation in the hybrid control strategy, the strictly saturated command signal is constructed with Sine saturation function. Based on the feature of the saturated command, an adaptive rate is introduced into the controller design to remove the effect of the input limitation theoretically. In order to improve the performance of the sliding phase, the terminal attractor is incorporated into the design of the ideal sliding surface. We perform numerical simulations to illustrate that the stabilization of the deployment is accomplished by the controller designed in spite of the input limitation.\par

>>>>

\begin{abstract}
This paper presents a novel adaptive dynamic sliding mode scheme for the deployment of the tethered satellite system. \textcolor{red}{To overcome the limited inputs of the dynamic model, a new scalable dimensionless transformation and strictly bounded terms are designed, which guarantee the existence of the ratio between limited inputs and command signals.} The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain. The stability analysis indicates that this measure can eliminate the uncertainty caused by the input limitation and guarantee the asymptotically stability of the deployment dynamics. \textcolor{red}{Finally, numerical simulations are presented to verify the effectiveness of the proposed control laws.}
\end{abstract}
\begin{keyword}
Tethered satellite system;  Sliding mode control;  Input limitation; Adaptive control
\end{keyword}
\end{frontmatter}
\section{Introduction}
The deployment is the key technology of the space tethered satellite system (TSS)~\cite{wen2008advances,yousefian2015anti}, which supports various applications for space explorations and scientific researches, such as space debris removals, space elevators, satellite de-orbits and the tethered space robots~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,huang2014optimal,Huang2016Impact,Huang201637,Huang2016}. \textcolor{red}{Many international space research institutes have launched orbital, suborbital and ground experiments, such as TSS-1R, SEDS, MAST and YES2, in an effort to verify the feasibility of the proposed theoretical and simulation schemes for the deployment of the TSS~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}. These experimental results intensively help researchers proceed to promote advanced mechanics, kinetic and control studies, to tackle the future challenges of space activities~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line,Xu2016Hybrid}.}\par

\textcolor{red}{Recent scientific researches about deployments of the TSS focus on the stabilization of the dynamics, and have provided different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approaches~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}.} Among these stabilization strategies, the hybrid tension and thruster control technique has been a great boost to new developments of the deployment of the TSS. Iki et al. implemented the ground deployment experiment, and utilized the thruster to conduct the deployment of a kilometers-length electrodynamic tether from a special spool-type reel~\cite{iki2014experiments}. \textcolor{red}{Aslanov et al. presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system was excited by a thruster force acting on the tug~\cite{aslanov2013dynamics}.} Huang~et~al. investigated the attitude and deployment dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}. Jung et al. adopted the thruster scheme to achieve the ideal deployment rate during the deployment of three-body tethered satellites~\cite{jung2015nonlinear}. \textcolor{red}{Liu et al. equipped the subsatellite with the thruster system, consisting of four pairs of thrusters, in order to regulate the attitude and deployment dynamics~\cite{liu2014attitude}. Zakrzhevskii divided the deployment process into two stages: in the first stage, the thruster was used to propel the subsatellite to the desired starting point of the next stage, and in the second stage, the tether was adjusted to the stable vertical configuration using tension generated by friction~\cite{zakrzhevskii2016method}. Mantellato et al. reported the thruster-aided deployment of tape tethers driven by both the tension and thruster forces~\cite{mantellato2015thrust}. These hybrid strategies has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, and thus is broadly utilized in engineering applications compared with other control strategies.}\par

However, there also exist some obstacles in the hybrid control design. Particularly, it's a prime problem that tension actuators and thrusters are both constrained by physical and chemical conditions, i.e., the tether is not available to be repressed like the stick, and meanwhile too big tether length rate might break the space tether. Also, the thruster can not provide the infinite propelling force~\cite{martinez1998spacecraft}. In simpler terms, the tension and thruster force for the tether deployment are both limited, and the view of control theory, the phenomena usually causes the input limitation of a dynamic system. Substituting limited inputs into unmodified conventional control scheme designed for systems with unlimited inputs results in poor performance or instability, and theoretically, such kind of implement is unreasonable. Hence to cope with the issues mentioned above, many scientific researchers spent much effort on the issue about input limitation of the TSS, providing many solutions on satellite arrangements and deployments. Huang et al. proposed an adaptive postcapture backstepping control of the tethered space robot, and analyzed the effect from constrained inputs by using specific auxiliary design systems~\cite{huang2015adaptive}. Wen et al. took into account the positive tension constraint by designing the feedback control with special saturation technique~\cite{wen2016constrained}, and Wen also proposed some remarkable achievements using optimal control for deployment~\cite{wen2008optimal}. Liu et al. reported the variable structure scheme for the deployment with thruster control, where the thruster is used to guarantee the positive tension during the mission~\cite{yingying2012variable}. In summary, existing studies deal with the major issue about the deployment with restricted tension and thruster force in two ways, accordingly, the suitable physical compensation and the elaborate design of limited input. In aspect of designing elaborate limited inputs, as Wen et al. explained, the limited terms, including the tension and the states of deployment dynamics, can be viewed as the solution of a nonlinear optimal control issue~\cite{wen2015tension}. \textcolor{red}{Hu reported an adaptive sliding mode control law with saturated input by using reduced sliding dynamic design approach~\cite{Hu2009Robust}, which requires an assumption that the command signal is bounded strictly, and for actual physical systems, this assumption always exits.} In this paper, a new dynamic adaptive saturated sliding mode  control for the deployment of the TSS is studied. For coping with the input saturation in the hybrid control strategy, the strictly saturated command signal is constructed with Sine saturation function. Based on the feature of the saturated command, an adaptive rate is introduced into the controller design to remove the effect of the input limitation theoretically. In order to improve the performance of the sliding phase, the terminal attractor is incorporated into the design of the ideal sliding surface. We perform numerical simulations to illustrate that the stabilization of the deployment is accomplished by the controller designed in spite of the input limitation.\par
